Dependent Object Types

### 2012-08-31 doc/candidacy/report.tex
context
a bit more context

Now, we can emulate this Tribe example in Scala at the expense of some
synctactic overhead, since further binding and ``out'' selection are
not native.
\lstinputlisting{tribe.scala}

>>>>

Now, we can emulate this Tribe example in Scala at the expense of some
syntactic overhead, since further binding and ``out'' selection are
not native. We use virtual types to ensure that the inner classes are
indeed ``virtual'', i.e. dynamically instead of statically
dispatched. In order to conform to the ``virtual class'' pattern, the
leaf classes \code{Graph} and \code{ColourGraph} are no longer in a
subclassing relationship with one another, as this would only bring
confusion when ascribing a coloured graph to a graph. Emulating
``out'' faithfully involves a bit of hackery in making Scala recognize
that, for example, \code{e.from.type} is a subtype of
\code{e.out.Node}. As noted in the paper, using ``out'' in library
code obscures the symmetry between the parameters (for example, in the
\code{distance} method below) but allows the family object to be
recovered without being explicitly passed around (contrast with the
method \code{distance2}).  \lstinputlisting{tribe.scala}
